
<div class = "page-dark-purple">

<div class = "wrap-columns">

<div class = "columns-35">

## Intentional Purchasing

Did your business implement any of the following policies, practices, or actions?

</div>
<div class = "columns-65">

```{r menu_q13}
menu_across_years(
  data = df_pmp_data,
  questions = df_questions_label,
  question_block = "q13",
  point_color = pmp_palette$`Dark purple`
)
```

</div>
</div>

</div>

<!-- Intentional Purchasing -->

<div class = "page-dark-purple">

<div class = "wrap-columns">

<div class = "columns-35">

## Intentional Purchasing

How many dollars did your business spend on purchases from businesses in the Portland Metro area that are BIPOC-owned and what percentage of your business’s purchases were from businesses in the Portland Metro area that are BIPOC-owned?

</div>
<div class = "columns-65">

```{r line_q16_18, fig.height = 5}
# compute percentage data
df_percent_data <- df_pmp_data |>
  select(year, percentage_purchase) |>
  # filter(!is.na(percentage_purchase) &
  #          percentage_purchase != "I'm not sure") |>
  separate(
    percentage_purchase,
    sep = "-",
    into = c("min_percent", "max_percent"),
    remove = FALSE
  ) |>
  # in 2024 we have a single percent a not a range
  mutate(
    max_percent = coalesce(max_percent, min_percent),
    min_percent = as.numeric(min_percent),
    max_percent = as.numeric(max_percent),
    labels = case_when(
      is.na(min_percent) ~ "Did not<br>track<br>%",
      TRUE ~ paste0(percentage_purchase, "%")
    ),
    labels_y = case_when(labels == "Did not<br>track<br>%" ~ 50, TRUE ~ max_percent + 5)
  )

# percentage plot
percent_plot <- ggplot(df_percent_data, colour = pmp_palette$`Dark teal`) +
  geom_bar(aes(x = year, y = 100),
           stat = "identity",
           fill = pmp_palette$`Mid teal`) +
  geom_bar(
    aes(x = year, y = max_percent),
    stat = "identity",
    fill = pmp_palette$`Light purple`,
    alpha = 1
  ) +
  geom_bar(
    aes(x = year, y = min_percent),
    stat = "identity",
    fill = pmp_palette$`Mid teal`,
    alpha = 0.5
  ) +
  ggtext::geom_textbox(
    aes(x = year, y = labels_y, label = labels),
    hjust = 0.5,
    halign = 0.5,
    family = "Gilroy ExtraBold",
    size = 7,
    colour = pmp_palette$`Light blue`,
    fill = NA,
    box.colour = NA
  ) +
  theme_minimal() +
  scale_x_continuous(limits = c(
    min(df_percent_data$year) - 0.5,
    max(df_percent_data$year) + 0.5
  ),
  breaks = unique(df_percent_data$year)) +
  theme(
    panel.background = element_rect(fill = pmp_palette$`Dark teal`, color = pmp_palette$`Dark teal`),
    plot.background = element_rect(fill = pmp_palette$`Dark teal`, color = pmp_palette$`Dark teal`),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    legend.position = "none",
    axis.title = element_blank(),
    panel.grid = element_blank()
  )

# same for amount data
df_amount_data <- df_pmp_data |>
  select(year, dollars_spent_purchases) |>
  mutate(
    na_labels = case_when(is.na(dollars_spent_purchases) ~ "Did not track<br>$", TRUE ~ ""),
    na_y_coord = case_when(
      is.na(dollars_spent_purchases) ~ 0,
      TRUE ~ dollars_spent_purchases
    )
  )

# amount plot
amount_plot <-
  ggplot(df_amount_data, aes(x = year, y = dollars_spent_purchases)) +
  geom_line(colour = pmp_palette$`Light blue`,
            size = 3,
            alpha = 0.3) +
  geom_point(
    aes(size = dollars_spent_purchases),
    colour = pmp_palette$`Dark teal`,
    fill = pmp_palette$`Light purple`,
    shape = 21,
    stroke = 4
  ) +
  ggtext::geom_textbox(
    aes(label = paste0(
      "$", grkmisc::pretty_num(dollars_spent_purchases)
    )),
    hjust = 0.5,
    halign = 0.5,
    vjust = -0.5,
    valign = 0,
    size = 12,
    family = "Gilroy ExtraBold",
    colour = pmp_palette$`Light blue`,
    box.colour = NA,
    fill = NA
  ) +
  ggtext::geom_textbox(
    aes(label = na_labels, x = year, y = na_y_coord),
    hjust = 0.5,
    halign = 0.5,
    vjust = 0,
    valign = 0,
    size = 8,
    family = "Gilroy ExtraBold",
    colour = pmp_palette$`Light blue`,
    box.colour = NA,
    fill = NA
  ) +
  scale_size(range = c(10, 20)) +
  scale_y_continuous(expand = expansion(mult = c(1, 2))) +
  scale_x_continuous(limits = c(
    min(df_percent_data$year) - 0.5,
    max(df_percent_data$year) + 0.5
  ),
  breaks = unique(df_percent_data$year)) +
  theme(
    panel.background = element_rect(fill = pmp_palette$`Dark teal`, color = pmp_palette$`Dark teal`),
    plot.background = element_rect(fill = pmp_palette$`Dark teal`, color = pmp_palette$`Dark teal`),
    axis.text.x = element_text(
      colour = pmp_palette$Teal,
      family = "Gilroy ExtraBold",
      size = 18
    ),
    axis.text.y = element_blank(),
    legend.position = "none",
    # instead of element_blank() we're making it disappear through colours to keep alignment
    axis.title = element_text(
      colour = pmp_palette$`Dark teal`,
      family = "Gilroy Medium",
      size = 10
    ),
    panel.grid = element_blank()
  )

# print plots
cowplot::plot_grid(amount_plot, percent_plot, ncol = 1, align = "v") +
  theme(plot.background = element_rect(fill = pmp_palette$`Dark teal`, color = pmp_palette$`Dark teal`))

```

</div>
</div>

</div>
