

<div class = "page-yellow">

<div class = "wrap-columns">

<div class = "columns-35">

## Work Experience in `r params$report_year + 1`

Which of the following internship and workplace experience programs does your business plan on implementing or continuing in `r params$report_year + 1`?

</div>
<div class = "columns-65-else">

```{r menu_q39}
menu_across_years(
  data = df_pmp_data,
  questions = df_questions_label,
  question_block = "q39",
  point_color = pmp_palette$Yellow
)

# else text
else_text_q39 <- df_pmp_data |>
  filter(year == params$report_year) |>
  pull(work_intern_other)
```

<span class="something-else"> `r knitr::asis_output(else_text_q39)` </span>

</div>
</div>

</div>

<!-- Work experience -->

<div class = "page-yellow">

<div class = "wrap-columns">

<div class = "columns-35">

## Work Experience in `r params$report_year + 1`

Which of the following policies, practices, or actions does your business plan on implementing or continuing in `r params$report_year + 1`?

</div>
<div class = "columns-65">

```{r menu_q40}
menu_across_years(
  data = df_pmp_data,
  questions = df_questions_label,
  question_block = "q40",
  point_color = pmp_palette$Yellow
)
```

</div>
</div>

</div>